**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study.

### 2017-06-01 doc/adaAbstract.Rmd
standard deviation output for gee instead of unit change

```{r correlation}
dsGEE <- ds %>% 
  dplyr::mutate(udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
                ageBase = ifelse(fVN == "Baseline", Age, NA),
                bmiBase = ifelse(fVN == "Baseline", BMI, NA),
                waistBase = ifelse(fVN == "Baseline", Waist, NA), 
                Sex = ifelse(Sex == "Male", 1, 0),
                Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
                Ethnicity = ifelse(Ethnicity == "European", 0, 1),
                fMedsBP = ifelse(fMedsBP == "Yes", 1, 0)
                # vitdBase = ifelse(fVN == "6Year", NA, VitaminD)
                ) %>% 
  dplyr::arrange(SID, fVN) %>% 
  dplyr::group_by(SID) %>% 
  tidyr::fill(udbpBase, ageBase, bmiBase, waistBase) %>% 
  dplyr::ungroup() %>%
  dplyr::arrange(SID, VN) %>% 
  dplyr::select(udbpBase, ACR, eGFR, VN, ageBase, Sex, Ethnicity, BMI, 
                Waist, DM, fMedsBP)

round(cor(dsGEE[sapply(dsGEE, is.numeric)], use = "complete.obs"), 2)

# Heatmap

corrplot::corrplot(cor(dsGEE[sapply(dsGEE, is.numeric)], use = "complete.obs"),
                   method = "color")

```

@@

gee <- ds %>%
  dplyr::mutate(
  udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
  ageBase = ifelse(fVN == "Baseline", Age, NA),
  DM = ifelse(DM == 1, "diabetes", "non_dia"),
  fDM = relevel(as.factor(DM), "non_dia"),
  Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
  Ethnicity = relevel(as.factor(Ethnicity), "Other")
  ) %>%
  dplyr::filter(!(fVN == "Baseline" &
                    acrStatus == "Macroalbuminuria")) %>%
  dplyr::filter(!(fVN == "Baseline" & eGFRStatus == "Moderate")) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%
  mason::design("gee") %>% 
  mason::add_settings(
      family = stats::gaussian(),
      corstr = 'ar1',
      cluster.id = 'SID'
    ) %>%
  mason::add_variables("yvars", c("ACR", "eGFR")) %>% 
  mason::add_variables("xvars", "UDBP") %>% 
  mason::add_variables("covariates", 
                       c("VN", "ageBase", "Sex", "Ethnicity", "BMI", "fDM")) %>% 
  mason::construct() %>%
  mason::scrub()
```

@@

gee %>% 
  dplyr::mutate(Xterms = term) %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(Yterms = factor(Yterms, 
                                levels = c("ACR", "eGFR"),
                                ordered = TRUE),
                Xterms = factor(Xterms,
                                levels = rev(c("<-Xterm",
                                           "VN",
                                           "ageBase",
                                           "SexMale",
                                           "EthnicityEuropean",
                                           "BMI",
                                           "fDMdiabetes")),
                                labels = rev(c("uVDBP",
                                           "Follow-up Duration",
                                           "Baseline Age",
                                           "Sex (male)",
                                           "Ethnicity (European)",
                                           "BMI",
                                           "Diabetes")),
                                ordered = TRUE)) %>% 
  arrange(Xterms) %>% 
  gee_plot(xlab = "Percent difference in outcome for every unit increase in uVDBP")
```

>>>>

@@

gee <- ds %>%
  dplyr::mutate(
    udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
    ageBase = ifelse(fVN == "Baseline", Age, NA),
    DM = ifelse(DM == 1, "diabetes", "non_dia"),
    fDM = relevel(as.factor(DM), "non_dia"),
    Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
    Ethnicity = relevel(as.factor(Ethnicity), "Other")
  ) %>% 
  dplyr::filter(!(fVN == "Baseline" &
                    acrStatus == "Macroalbuminuria")) %>%
  dplyr::filter(!(fVN == "Baseline" & eGFRStatus == "Moderate")) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  # dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%
  mason::design("gee") %>% 
  mason::add_settings(
      family = stats::gaussian(),
      corstr = 'ar1',
      cluster.id = 'SID'
    ) %>%
  mason::add_variables("yvars", c("ACR", "eGFR")) %>% 
  mason::add_variables("xvars", "UDBP") %>% 
  mason::add_variables("covariates", c("VN", "ageBase", "Sex", "Ethnicity", "BMI", "fDM")) %>% 
  mason::construct() %>%
  mason::scrub() %>% 
  mason::polish_transform_estimates(function(x) (exp(x) - 1) * 100) %>%
  dplyr::select(Yterms, Xterms, term, estimate, conf.low, conf.high, p.value)
```

@@

gee %>% 
  dplyr::mutate(Xterms = term) %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(Yterms = factor(Yterms, 
                                levels = c("ACR", "eGFR"),
                                ordered = TRUE),
                Xterms = factor(Xterms,
                                levels = rev(c("<-Xterm",
                                           "VN",
                                           "ageBase",
                                           "SexMale",
                                           "EthnicityEuropean",
                                           "BMI",
                                           "fDMdiabetes")),
                                labels = rev(c("uVDBP",
                                           "Follow-up Duration",
                                           "Baseline Age",
                                           "Sex (male)",
                                           "Ethnicity (European)",
                                           "BMI",
                                           "Diabetes")),
                                ordered = TRUE)) %>% 
  arrange(Xterms) %>% 
  gee_plot(xlab = "Percent difference with 95% CI in outcome for every SD increase in uVDBP and covariates")
```
